Case Study: ChIP-seq Differential Peak Calling

### 2018-02-22 datasets/ChIP-seq/ChIP-seq.Rmd
Fix typo in ChIP-seq case study code

## project data/results folders
datdir <- "data"
resdir <- "results"
dir.create(datdir, showWarnings = FALSE)
dir.create(residr, showWarnings = FALSE)

>>>>

## project data/results folders
datdir <- "data"
resdir <- "results"
dir.create(datdir, showWarnings = FALSE)
dir.create(resdir, showWarnings = FALSE)
